---
title: "Developing Data Products - Fantasy Football Exploratory Data"
author: "Joshua Peterson"
date: "11/09/2016"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Project Objective
This is the final project for the Coursera course, Developing Data Products.  This project includes

- A shiny app deployed on RStudio
- A quick presentation describing the app

The link to the app can be found here https://portfoliomanager.shinyapps.io/AndrewLuckPerforman/

##Shiny App Use

- Do you own a fantasy football team?!
- Are you super competitive?
- Are you tired of making seemingly "random" decisions
- Are you tired of hearing constant smack from the rest of your league?

This may be the app for you.  In a quick snapshot you can gain insight in to passing yards based off of predictors such as:

- Opponent defensive rank
- Opponent
- Location of the game (home or away), and finally

##Data Variables
Snapshot summary of the statistics for Andrew Luck, quarterback for the Indianopolis Colts...and one of my top fantasy performers.
```{r, echo=FALSE, comment="", message=FALSE}
library(readr)
AL <- read_csv("Andrew_Luck_2016.csv")
ALdf<- as.data.frame(AL)
summary(ALdf)
```

##Fantasy Football Output Goodness
An example of the output shown is Luck's passing yards against four predictor variables

```{r, echo=FALSE, comment="", message=FALSE}
library(plotly)
plot_ly(ALdf, x= ~Def.Rank.Yds, y= ~PassYds, type = 'box', name = "Pass Yards") %>%
   layout(yaxis = list(title = "Yards"), barmode = "group")
```


