---
title: "Fantasy Player Analysis - Frank Gore"
author: "Joshua Peterson"
date: "11/6/2016"
output: html_document
---

Player analysis and selection for the week of 11.4.2016

```{r, echo=FALSE}

RushydsPts<- 1/10
RushtdPts<- 6
RecydsPts<- 1/10
RectdPts<- 6

```

QB Analysis - Pull Player Data
```{r, echo=FALSE, comment= "", message=FALSE}
library(readr)
FG <- read_csv("~/Fantasy-Football-Models/Gore_2016.csv")
FGdf<- as.data.frame(FG)
```

# QB Analysis

## Luck - Summary Passing Data

Luck Yards Summary
```{r, echo=FALSE, comment="", message=FALSE}
summary(FGdf)
```

## Exploratory data analysis

Location analysis (Pass Yards and Rush Yards)
```{r, echo=FALSE, comment= "", message=FALSE}

plot_ly(FGdf, x= ~Location, y= ~RushYds, type = 'box', name = "Rush Yards") %>%
  layout(yaxis = list(title = "Yards"), barmode = "group")

plot_ly(FGdf, x= ~Location, y= ~RecYds, type = 'box', name = "Rec Yards") %>%
  layout(yaxis = list(title = "Yards"), barmode = "group")

```

### Location analysis (TDs and Interceptions)

```{r, echo=FALSE, comment= "", message=FALSE}

plot_ly(FGdf, x= ~Location, y= ~RushTD, type = 'box', name = "Rush TDs") %>%
  layout(yaxis = list(title = "Number"), barmode = "group")
  
plot_ly(FGdf, x= ~Location, y= ~RecTD, type = 'box', name = "Rec TDs") %>%
  layout(yaxis = list(title = "Number"), barmode = "group")

```

### Opponent Analysis

Opponent vs. Pass Yards
```{r, echo=FALSE, comment="", message=FALSE}
par(mfrow = c(5,1), mar = c(4,4,1,1))
plot_ly(FGdf, x = ~Opp, y = ~RushYds, type = "box")
plot_ly(FGdf, x = ~Opp, y = ~RecYds, type = "box")

```

### Conference Game Analysis

Conference analysis (Pass Yards and Rush Yards)
```{r, echo=FALSE, comment="", message=FALSE}

plot_ly(ALdf, x= ~ConfGame, y= ~PassYds, type = 'bar', name = "Pass Yards") %>%
  add_trace(y = ~RushYds, name = "RushYds") %>%
  layout(yaxis = list(title = "Yards"), barmode = "group")

```

Conference analysis (TDs and Interceptions)
```{r, echo=FALSE, comment="", message=FALSE}

plot_ly(ALdf, x= ~ConfGame, y= ~PassTD, type = 'bar', name = "Pass TDs") %>%
  add_trace(y = ~RushTd, name = "Rush TDs") %>%
  add_trace(y = ~Int, name = "Interceptions") %>%
  layout(yaxis = list(title = "Number"), barmode = "group")

```

### Defensive Ranking Analysis

Defense rank vs. Pass Yards
```{r, echo=FALSE, message=FALSE, comment=""}
library(ggplot2)
par(mfrow = c(5,2), mar = c(4,4,1,1))
plot1<-qplot(Def.Rank.Yds,RushYds, data = FGdf) + geom_smooth(method = "lm")
plot2<-qplot(Def.Rank.Yds, RecYds, data = FGdf) + geom_smooth(method = "lm")

(g1<- ggplotly(plot1))
(g2<- ggplotly(plot2))

```

Gore Yards LSE
```{r, echo=FALSE, comment="", message=FALSE}
par(mfrow = c(3,2), mar = c(4,4,2,1))
hist(FGdf$RushYds,col="blue",breaks=100, main = "Histogram of Gore Rush Yds/Game",xlab = "Pass Yds/Game")
hist(FGdf$RecYds,col="red",breaks=100, main = "Histogram of Gore Receiving Yds/Game",xlab = "Yards/Game")  
hist(FGdf$RushTD,col="purple",breaks=100, main = "Histogram of Gore Rush TDs/Game",xlab = "TDs/Game")
hist(FGdf$RecTD,col="grey",breaks=100, main = "Histogram of Gore Receiving TDs/Game",xlab = "TDs/Game")

```

## Linear model fitting

### Model fitting vs. Location

Rush Yds vs. Location
```{r, echo=FALSE, comment="", message=FALSE}
FGfitRushYdsLoc<- lm(RushYds ~ Location, data = FGdf)
summary(FGfitRushYdsLoc)

```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrLoc<- data.frame(Location="Away", data=FGdf)
LocLmPredictRy<- head(predict(FGfitRushYdsLoc, CurrLoc, interval="predict"))
LocLmPredictRy
```

Receiving Yds. vs. Location
```{r, echo=FALSE, comment="", message=FALSE}
FGfitRecYdsLoc<- lm(RecYds ~ Location, data = FGdf)
summary(FGfitRecYdsLoc)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrLoc<- data.frame(Location="Away", data=FGdf)
LocLmPredictRy<- head(predict(FGfitRecYdsLoc, CurrLoc, interval="predict"))
LocLmPredictRy
```

Rush TDs. vs. Location
```{r, echo=FALSE, comment="", message=FALSE}
FGfitRushTDLoc<- lm(RushTD ~ Location, data = FGdf)
summary(FGfitRushTDLoc)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrLoc<- data.frame(Location="Away", data=FGdf)
LocLmPredictRuTd<- head(predict(FGfitRushTDLoc, CurrLoc, interval="predict"))
LocLmPredictRuTd
```

Recieving TDs vs. Location
```{r, echo=FALSE, comment="", message=FALSE}
FGfitRecTDLoc<- lm(RecTD ~ Location, data = FGdf)
summary(FGfitRecTDLoc)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrLoc<- data.frame(Location="Away", data=FGdf)
LocLmPredictRecTd<- head(predict(FGfitRecTDLoc, CurrLoc, interval="predict"))
LocLmPredictRecTd
```


#### Model fitting vs. opponent

Rush Yards vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
FGfitRushYds<- lm(RushYds ~ Opp, data = FGdf)
summary(FGfitRushYds)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(Opp="GNB", data=FGdf)
OppLmPredictRuy<- head(predict(FGfitRushYds, CurrOpp, interval="predict"))
OppLmPredictRuy
```

Recieving Yards vs. opponent data

```{r, echo=FALSE, comment="", message=FALSE}
FGfitRushYds<- lm(RecYds ~ Opp, data = FGdf)
summary(FGfitRushYds)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(Opp="GNB", data=FGdf)
OppLmPredictRecy<- head(predict(FGfitRushYds, CurrOpp, interval="predict"))
OppLmPredictRecy
```

Rush TDs vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
FGfitRushTD<- lm(RushTD ~ Opp, data = FGdf)
summary(FGfitRushTD)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(Opp="GNB", data=FGdf)
OppLmPredictRut<- head(predict(FGfitRushTD, CurrOpp, interval="predict"))
OppLmPredictRut
```

Recieving TDs vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
FGfitRecTD<- lm(RecTD ~ Opp, data = FGdf)
summary(FGfitRecTD)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(Opp="GNB", data=FGdf)
OppLmPredictRect<- head(predict(FGfitRecTD, CurrOpp, interval="predict"))
OppLmPredictRect
```

#### Model fitting vs. Conference Game

Pass Yards vs. conference data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitPassYds<- lm(PassYds ~ ConfGame, data = ALdf)
summary(ALfitPassYds)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(ConfGame="NonConf", data=ALdf)
OppLmPredictPy<- head(predict(ALfitPassYds, CurrOpp, interval="predict"))
OppLmPredictPy
```

Rush Yards vs. opponent data

```{r, echo=FALSE, comment="", message=FALSE}
ALfitRushYds<- lm(RushYds ~ ConfGame, data = ALdf)
summary(ALfitRushYds)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(ConfGame="NonConf", data=ALdf)
OppLmPredictRy<- head(predict(ALfitRushYds, CurrOpp, interval="predict"))
OppLmPredictRy
```

Pass TDs vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitPassTD<- lm(PassTD ~ ConfGame, data = ALdf)
summary(ALfitPassTD)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(ConfGame="NonConf", data=ALdf)
OppLmPredictPt<- head(predict(ALfitPassTD, CurrOpp, interval="predict"))
OppLmPredictPt
```

Rush TDs vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitRushTD<- lm(RushTd ~ ConfGame, data = ALdf)
summary(ALfitRushTD)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(ConfGame="NonConf", data=ALdf)
OppLmPredictRt<- head(predict(ALfitRushTD, CurrOpp, interval="predict"))
OppLmPredictRt
```

Interceptions vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitInt<- lm(Int ~ ConfGame, data = ALdf)
summary(ALfitInt)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(ConfGame="NonConf", data=ALdf)
OppLmPredictInt<- head(predict(ALfitInt, CurrOpp, interval="predict"))
OppLmPredictInt
```

### Model fitting vs. defensive rank

Rush Yards vs. Defensive Rank
```{r, echo=FALSE, comment="", message=FALSE}
FGfitRushYdsRnk<- lm(RushYds ~ Def.Rank.Yds, data = FGdf)
summary(FGfitRushYdsRnk)

cor(FGdf$RushYds, FGdf$Def.Rank.Yds)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=8, data=FGdf)
RankLmPredictRuy<- head(predict(FGfitRushYdsRnk, CurrRank, interval="predict"))
RankLmPredictRuy
```

Recieving Yards vs. Defensive Rank
```{r, echo=FALSE, comment="", message=FALSE}
FGfitRecYdsRnk<- lm(RecYds ~ Def.Rank.Yds, data = FGdf)
summary(FGfitRecYdsRnk)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=8, data=FGdf)
RankLmPredictRecy<- head(predict(FGfitRecYdsRnk, CurrRank, interval="predict"))
RankLmPredictRecy
```

Rush TDs vs. Defensive Rank
```{r, echo=FALSE, comment="", message=FALSE}
FGfitRushTDRnk<- lm(RushTd ~ Def.Rank.Yds, data = ALdf)
summary(FGfitRushTDRnk)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=8, data=FGdf)
RankLmPredictRut<- head(predict(FGfitRushTDRnk, CurrRank, interval="predict"))
RankLmPredictRut
```

Receiving TDs vs. Defensive Rank
```{r, echo=FALSE, comment="", message=FALSE}
ALfitRecTDRnk<- lm(RecTD ~ Def.Rank.Yds, data = FGdf)
summary(ALfitRecTDRnk)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=8, data=FGdf)
RankLmPredictRect<- head(predict(ALfitRecTDRnk, CurrRank, interval="predict"))
RankLmPredictRect
```

## Machine Learning Alogorithm (Rush Yards)

### Data Splitting

In this data splitting action, I am splitting the data into 60% training set and 40% testing set.
```{r, echo=FALSE, comment="", message=FALSE}
library(caret)
library(lattice)

summary(FGdf)
inTrain <- createDataPartition(y=FGdf$RushYds,p=0.60, list=FALSE)
training <- FGdf[inTrain,]
testing <- FGdf[-inTrain,]
dim(training); dim(testing)
```

## K-Fold Cross Validation

We will then use the K-Fold process to cross-validate the data by splitting the training set in to many, smaller data sets.

Here, I am creating 10 folds and setting a random number seed of 32323 for the study. Each fold has approximately the same number of samples in it.
```{r, echo=FALSE, comment="", message=FALSE}
set.seed(32323)
Passfolds <- createFolds(y=FGdf$RushYds,k=10,list=TRUE,returnTrain=TRUE)
sapply(Passfolds,length)
Passfolds[[1]][1:10]
```

## Machine learning alogorithm decisioning

First I wanted to determine the optimal machine learning model to use.  The first test I used the Decision Tree approach.  I followed up by testing the Random Forest approach.

### Machine learning using Decision Trees

The first task was to determine model fit.
```{r, echo=FALSE, comment="", message=FALSE}
library(rpart)
modelFitRush <- rpart(RushYds ~ Def.Rank.Yds, data = FGdf, method = "anova")
```

Next, construct a Decision Tree graph
```{r, echo=FALSE, comment="", message=FALSE}
fancyRpartPlot(modelFitRush)
```

## Machine Learning Alogorithm (Rush Yards)

### Data Splitting

In this data splitting action, I am splitting the data into 60% training set and 40% testing set.
```{r, echo=FALSE, comment="", message=FALSE}
summary(FGdf)
inTrain <- createDataPartition(y=FGdf$RecYds,p=0.60, list=FALSE)
training <- FGdf[inTrain,]
testing <- FGdf[-inTrain,]
dim(training); dim(testing)
```

We will then use the K-Fold process to cross-validate the data by splitting the training set in to many, smaller data sets.

Here, I am creating 10 folds and setting a random number seed of 32323 for the study. Each fold has approximately the same number of samples in it.
```{r, echo=FALSE, comment="", message=FALSE}
set.seed(32323)
Passfolds <- createFolds(y=FGdf$RecYds,k=10,list=TRUE,returnTrain=TRUE)
sapply(Passfolds,length)
Passfolds[[1]][1:10]
```

Decision tree model fit Rush Yards Defense Rank.
```{r, echo=FALSE, comment="", message=FALSE}
modelFitRec <- rpart(RecYds ~ Def.Rank.Yds, data = FGdf, method = "anova")
```

Pass Yards decision tree graph
```{r, echo=FALSE, comment="", message=FALSE}
fancyRpartPlot(modelFitRec)
```


### Machine learning using Decision Trees

The first task was to determine model fit.
```{r, echo=FALSE, comment="", message=FALSE}
modelFitPass <- rpart(RushYds ~ Def.Rank.Yds, data = ALdf, method = "anova")
```

### Output from Decision Tree Model vs. Yards Passing

Current week (9) opponent Green Bay Packers.  The defense is currently ranked # 8 according to www.pro-football-reference.com.

According to the model, there is a 27% chance that Gore will run for 63 yards.  This takes in to account defense rank ONLY.  There is an 42.0% chance Gore will have 14 receiving 24 yards.  Once again this takes in to account defense rank ONLY.

We will now use the LM model for prediction (Rush Yds)
```{r, echo=FALSE, comment="", message=FALSE}
lmModel<- lm(formula = RushYds ~ Opp+Def.Rank.Yds+Location, data = FGdf)
currdata = data.frame(Opp="GNB",Def.Rank.Yds=8,Location="Away",data=ALdf)
rush_predict_final<- predict(lmModel, currdata)
rush_predict_final
```

Predicted passing points
```{r, echo=FALSE, comment="", message=FALSE}
RushPts<-rush_predict_final*RushydsPts
RushPts
```

We will now use the LM model for prediction (Receiving Yds)
```{r, echo=FALSE, comment="", message=FALSE}
lmModel<- lm(formula = RecYds ~ Opp+Def.Rank.Yds+Location, data = FGdf)
currdata = data.frame(Opp="GNB", Def.Rank.Yds=7, Location="Away",data=FGdf)
rec_predict_final<- predict(lmModel, currdata)
rec_predict_final
```

Predicted rushing points
```{r, echo=FALSE, comment="", message=FALSE}
RecPts<-rec_predict_final*RecydsPts
RecPts
```

We will now use the LM model for prediction (Rush TDs)
```{r, echo=FALSE, comment="", message=FALSE}
lmModel<- lm(formula = RushTD ~ Opp+Def.Rank.Yds+Location, data = FGdf)
currdata = data.frame(Opp="GNB", Def.Rank.Yds=8, Location="Away",data=FGdf)
RusTd_predict_final<- predict(lmModel, currdata)
RusTd_predict_final
```

Predicted rushing points
```{r, echo=FALSE, comment="", message=FALSE}
TdRusPts<-RusTd_predict_final*RushtdPts
TdRusPts
```

We will now use the LM model for prediction (Recieving TDs)
```{r, echo=FALSE, comment="", message=FALSE}
lmModel<- lm(formula = RecTD ~ Opp+Def.Rank.Yds+Location, data = FGdf)
currdata = data.frame(Opp="GNB", Def.Rank.Yds=8, Location="Away",data=FGdf)
recTd_predict_final<- predict(lmModel, currdata)
recTd_predict_final
```

Predicted rushing TD points
```{r, echo=FALSE, comment="", message=FALSE}
TdRecPts<-recTd_predict_final*RectdPts
TdRecPts
```

Total predicted points using linear regression models
```{r, echo=FALSE, comment="", message=FALSE}
FGTotalPer<- RushPts+RecPts+TdRushPts+TdRecPts
FGTotalPer
```

Outcome:  Gore's predicted point total for Week 9 against the Green Bay Packers is 16.50 points.  NFL.com is predicting that Gore's point total will be 6.8 points.

Actual points scored, 19.10 a 2.6 point delta than predicted.

```{r, echo=FALSE, comment="", message=FALSE}
library(knitr)
knit("Gore_Quant Analysis_2016.Rmd")
```
