---
title: "Fantasy Player Analysis - Andrew Luck"
author: "Joshua Peterson"
date: "11/4/2016"
output: html_document
---

Player analysis and selection for the week of 11.4.2016

```{r, echo=FALSE}
PassydsPts<- 1/25
PasstdPts<- 4
Int<- -2
RushydsPts<- 1/10
RushtdPts<- 6
```

QB Analysis - Pull Player Data
```{r, echo=FALSE, comment= "", message=FALSE}
library(readr)
AL <- read_csv("~/Fantasy-Football-Models/Andrew_Luck_2016.csv")
ALdf<- as.data.frame(AL)
```

# QB Analysis

## Luck - Summary Passing Data

Luck Yards Summary
```{r, echo=FALSE, comment="", message=FALSE}
summary(ALdf)
```

## Fitting models

### Distribution of Pass Yards

Plotting a normal distribution curve (Pass Yards)
```{r, echo=FALSE, comment= "", message=FALSE}
x<- ALdf$PassYds
NMPass<- hist(ALdf$PassYds, breaks = 20, col="red")
xfit<- seq(min(x), max(x), length=40)
yfit<- dnorm(xfit, mean = mean(x), sd=sd(x))
yfit<- yfit*diff(NMPass$mids[1:2])*length(x)
lines(xfit, yfit, col="blue", lwd=2)
```

Skew
```{r, echo=FALSE, comment= "", message=FALSE}
skewness(x)
```

Kurtosis
```{r, echo=FALSE, comment= "", message=FALSE}
kurtosis(x)
```

Data does not appear to fall along the normal, possibly double exponential distribution curve.  We can see evidence of left leaning skew and slightly negative kurtoctic.

Standard deviation of Pass Yds
```{r, echo=FALSE, comment= "", message=FALSE}
sd(ALdf$PassYds)
```

Plotting an emperical cumulative distribution curve (Pass Yds)
```{r, echo=FALSE, comment= "", message=FALSE}
x.normPass<- rnorm(n=62, m=270.8, sd=75.35)
plot(density(x.normPass), main="Density estimate of data")

plot.ecdf(x.normPass, main = "Empirical cumulative distribution curve", xlab = "Passing Yards")
```

Summary of Density Estimate (Pass Yds)
```{r, echo=FALSE, comment= "", message=FALSE}
density(x.normPass)
```

Shape of the density estimate data curve suggests normal distribution.

Passing Yards Quantile-Quantile (Q-Q) plot (Pass Yds)
```{r, echo=FALSE, comment= "", message=FALSE}
z.normPass<- x.normPass-mean(x.normPass)/sd(x.normPass)
qqnorm(z.normPass)
abline(265,75)
```

## Conclusion

After running the series of model tests, it is assumed that a normal distribution model for Pass Yards will be the best model fit.

### Distribution of Rush Yards

Plotting a normal distribution curve (Pass Yards)
```{r, echo=FALSE, comment= "", message=FALSE}
y<- ALdf$RushYds
NMRush<- hist(ALdf$RushYds, breaks = 20, col="red")
xfit<- seq(min(y), max(y), length=40)
yfit<- dnorm(xfit, mean = mean(y), sd=sd(y))
yfit<- yfit*diff(NMRush$mids[1:2])*length(y)
lines(xfit, yfit, col="blue", lwd=2)
```

Skew
```{r, echo=FALSE, comment= "", message=FALSE}
skewness(y)
```

Kurtosis
```{r, echo=FALSE, comment= "", message=FALSE}
kurtosis(y)
```

Data shows a bit more skewness (0.21) vs. Pass Yards (0.14).  Distribution falls between norman and double exponential distributions.  Distribution is flat as evidenced by the slightly negative kurtosis of the curve.

Plotting an emperical cumulative distribution curve (Rush Yds)

Standard deviation (Rush Yds)
```{r, echo=FALSE, comment= "", message=FALSE}
sd(ALdf$RushYds)
```

```{r, echo=FALSE, comment= "", message=FALSE}
x.normRush<- rnorm(n=62, m=20.18, sd=12.50)
plot(density(x.normRush), main="Density estimate of data")

plot.ecdf(x.normRush, main = "Empirical cumulative distribution curve", xlab = "Rushing Yards")
```

Summary of Density Estimate (Rush Yds)
```{r, echo=FALSE, comment= "", message=FALSE}
density(x.normRush)
```

Shape of the density estimate data curve suggests normal distribution.

Passing Yards Quantile-Quantile (Q-Q) plot (Pass Yds)
```{r, echo=FALSE, comment= "", message=FALSE}
z.normRush<- x.normRush-mean(x.normRush)/sd(x.normRush)
qqnorm(z.normRush)
abline(19,11)
```

## Conclusion

After running the series of model tests, it is assumed that a normal distribution model for Rush Yards will be the best model fit.

## Exploratory data analysis

Location analysis (Pass Yards and Rush Yards)
```{r, echo=FALSE, comment= "", message=FALSE}

plot_ly(ALdf, x= ~Location, y= ~PassYds, type = 'box', name = "Pass Yards") %>%
  add_trace(y = ~RushYds, name = "RushYds") %>%
  layout(yaxis = list(title = "Yards"), barmode = "group")

```

### Location analysis (TDs and Interceptions)

```{r, echo=FALSE, comment= "", message=FALSE}

plot_ly(ALdf, x= ~Location, y= ~PassTD, type = 'box', name = "Pass TDs") %>%
  add_trace(y = ~RushTd, name = "Rush TDs") %>%
  add_trace(y = ~Int, name = "Interceptions") %>%
  layout(yaxis = list(title = "Number"), barmode = "group")

```



### Opponent Analysis

Opponent vs. Pass Yards
```{r, echo=FALSE, comment="", message=FALSE}
par(mfrow = c(5,1), mar = c(4,4,1,1))
plot_ly(ALdf, x = ~Opp, y = ~PassYds, type = "box")
plot_ly(ALdf, x = ~Opp, y = ~RushYds, type = "box")
plot_ly(ALdf, x = ~Opp, y = ~PassTD, type = "box")
plot_ly(ALdf, x = ~Opp, y = ~RushTd, type = "box")
plot_ly(ALdf, x = ~Opp, y = ~Int, type = "box")
```

### Conference Game Analysis

Conference analysis (Pass Yards and Rush Yards)
```{r, echo=FALSE, comment="", message=FALSE}

plot_ly(ALdf, x= ~ConfGame, y= ~PassYds, type = 'bar', name = "Pass Yards") %>%
  add_trace(y = ~RushYds, name = "RushYds") %>%
  layout(yaxis = list(title = "Yards"), barmode = "group")

```

Conference analysis (TDs and Interceptions)
```{r, echo=FALSE, comment="", message=FALSE}

plot_ly(ALdf, x= ~ConfGame, y= ~PassTD, type = 'bar', name = "Pass TDs") %>%
  add_trace(y = ~RushTd, name = "Rush TDs") %>%
  add_trace(y = ~Int, name = "Interceptions") %>%
  layout(yaxis = list(title = "Number"), barmode = "group")

```

### Defensive Ranking Analysis

Defense rank vs. Pass Yards
```{r, echo=FALSE, message=FALSE, comment=""}
library(ggplot2)
par(mfrow = c(5,2), mar = c(4,4,1,1))
plot1<-qplot(Def.Rank.Yds,PassYds, data = ALdf) + geom_smooth(method = "lm")
plot2<-qplot(Def.Rank.Yds, RushYds, data = ALdf) + geom_smooth(method = "lm")
plot3<-qplot(Def.Rank.Yds, PassTD, data = ALdf) + geom_smooth(method = "lm")
plot4<-qplot(Def.Rank.Yds, RushTd, data = ALdf) + geom_smooth(method = "lm")
plot5<-qplot(Def.Rank.Yds, Int, data = ALdf) + geom_smooth(method = "lm")

(g1<- ggplotly(plot1))
(g2<- ggplotly(plot2))
(g3<- ggplotly(plot3))
(g4<- ggplotly(plot4))
(g5<- ggplotly(plot5))
```

Luck Yards LSE
```{r, echo=FALSE, comment="", message=FALSE}
par(mfrow = c(3,2), mar = c(4,4,2,1))
hist(ALdf$PassYds,col="blue",breaks=15, main = "Histogram of Luck Pass Yds/Game",xlab = "Yards/Game")
hist(ALdf$RushYds,col="red",breaks=15, main = "Histogram of Luck Rush Yds/Game",xlab = "Yards/Game")  
hist(ALdf$PassTD,col="purple",breaks=5, main = "Histogram of Luck Pass TDs/Game",xlab = "TDs/Game")
hist(ALdf$RushTd,col="grey",breaks=5, main = "Histogram of Luck Rush TDs/Game",xlab = "TDs/Game")
hist(ALdf$Int,col="grey",breaks=5, main = "Histogram of Luck Interceptions/Game",xlab = "Interceptions/Game")
```

## Linear model fitting

### Model fitting vs. Location

Pass Yds vs. Location
```{r, echo=FALSE, comment="", message=FALSE}
ALfitPassYdsLoc<- lm(PassYds ~ Location, data = ALdf)
summary(ALfitPassYdsLoc)
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrLoc<- data.frame(Location="Home", data=ALdf)
LocLmPredictPy<- head(predict(ALfitPassYdsLoc, CurrLoc, interval="predict"),1)
LocLmPredictPy
```



Rush Yds. vs. Location
```{r, echo=FALSE, comment="", message=FALSE}
ALfitRushYdsLoc<- lm(RushYds ~ Location, data = ALdf)
summary(ALfitRushYdsLoc)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrLoc<- data.frame(Location="Home", data=ALdf)
LocLmPredictRy<- head(predict(ALfitRushYdsLoc, CurrLoc, interval="predict"),1)
LocLmPredictRy
```

Pass TDs. vs. Location
```{r, echo=FALSE, comment="", message=FALSE}
ALfitPassTDLoc<- lm(PassTD ~ Location, data = ALdf)
summary(ALfitPassTDLoc)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrLoc<- data.frame(Location="Home", data=ALdf)
LocLmPredictPt<- head(predict(ALfitPassTDLoc, CurrLoc, interval="predict"),1)
LocLmPredictPt
```

Rush TDs vs. Location
```{r, echo=FALSE, comment="", message=FALSE}
ALfitRushTDLoc<- lm(RushTd ~ Location, data = ALdf)
summary(ALfitRushTDLoc)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrLoc<- data.frame(Location="Home", data=ALdf)
LocLmPredictRt<- head(predict(ALfitRushTDLoc, CurrLoc, interval="predict"),1)
LocLmPredictRt
```


#### Model fitting vs. opponent

Pass Yards vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitPassYds<- lm(PassYds ~ Opp, data = ALdf)
summary(ALfitPassYds)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(Opp="TEN", data=ALdf)
OppLmPredictPy<- head(predict(ALfitPassYds, CurrOpp, interval="predict"),1)
OppLmPredictPy
```

Rush Yards vs. opponent data

```{r, echo=FALSE, comment="", message=FALSE}
ALfitRushYds<- lm(RushYds ~ Opp, data = ALdf)
summary(ALfitRushYds)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(Opp="TEN", data=ALdf)
OppLmPredictRy<- head(predict(ALfitRushYds, CurrOpp, interval="predict"))
OppLmPredictRy
```

Pass TDs vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitPassTD<- lm(PassTD ~ Opp, data = ALdf)
summary(ALfitPassTD)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(Opp="TEN", data=ALdf)
OppLmPredictPt<- head(predict(ALfitPassTD, CurrOpp, interval="predict"))
OppLmPredictPt
```

Rush TDs vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitRushTD<- lm(RushTd ~ Opp, data = ALdf)
summary(ALfitRushTD)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(Opp="TEN", data=ALdf)
OppLmPredictRt<- head(predict(ALfitRushTD, CurrOpp, interval="predict"))
OppLmPredictRt
```

Interceptions vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitInt<- lm(Int ~ Opp, data = ALdf)
summary(ALfitInt)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(Opp="TEN", data=ALdf)
OppLmPredictInt<- head(predict(ALfitInt, CurrOpp, interval="predict"))
OppLmPredictInt
```

#### Model fitting vs. Conference Game

Pass Yards vs. conference data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitPassYds<- lm(PassYds ~ ConfGame, data = ALdf)
summary(ALfitPassYds)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(ConfGame="Conf", data=ALdf)
OppLmPredictPy<- head(predict(ALfitPassYds, CurrOpp, interval="predict"))
OppLmPredictPy
```

Rush Yards vs. opponent data

```{r, echo=FALSE, comment="", message=FALSE}
ALfitRushYds<- lm(RushYds ~ Conf, data = ALdf)
summary(ALfitRushYds)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(ConfGame="Conf", data=ALdf)
OppLmPredictRy<- head(predict(ALfitRushYds, CurrOpp, interval="predict"))
OppLmPredictRy
```

Pass TDs vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitPassTD<- lm(PassTD ~ ConfGame, data = ALdf)
summary(ALfitPassTD)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(ConfGame="NonConf", data=ALdf)
OppLmPredictPt<- head(predict(ALfitPassTD, CurrOpp, interval="predict"))
OppLmPredictPt
```

Rush TDs vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitRushTD<- lm(RushTd ~ ConfGame, data = ALdf)
summary(ALfitRushTD)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(ConfGame="NonConf", data=ALdf)
OppLmPredictRt<- head(predict(ALfitRushTD, CurrOpp, interval="predict"))
OppLmPredictRt
```

Interceptions vs. opponent data
```{r, echo=FALSE, comment="", message=FALSE}
ALfitInt<- lm(Int ~ ConfGame, data = ALdf)
summary(ALfitInt)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrOpp<- data.frame(ConfGame="NonConf", data=ALdf)
OppLmPredictInt<- head(predict(ALfitInt, CurrOpp, interval="predict"))
OppLmPredictInt
```

### Model fitting vs. defensive rank

Pass Yards vs. Defensive Rank
```{r, echo=FALSE, comment="", message=FALSE}
ALfitPassYdsRnk<- lm(PassYds ~ Def.Rank.Yds, data = ALdf)
summary(ALfitPassYdsRnk)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=17, data=ALdf)
RankLmPredictPy<- head(predict(ALfitPassYdsRnk, CurrRank, interval="predict"),1)
RankLmPredictPy
```

Rush Yards vs. Defensive Rank
```{r, echo=FALSE, comment="", message=FALSE}
ALfitRushYdsRnk<- lm(RushYds ~ Def.Rank.Yds, data = ALdf)
summary(ALfitRushYdsRnk)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=17, data=ALdf)
RankLmPredictRy<- head(predict(ALfitRushYdsRnk, CurrRank, interval="predict"))
RankLmPredictRy
```

Pass TDs vs. Defensive Rank
```{r, echo=FALSE, comment="", message=FALSE}
ALfitPassTDRnk<- lm(PassTD ~ Def.Rank.Yds, data = ALdf)
summary(ALfitPassTDRnk)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=17, data=ALdf)
RankLmPredictPt<- head(predict(ALfitPassTDRnk, CurrRank, interval="predict"))
RankLmPredictPt
```

Rush TDs vs. Defensive Rank
```{r, echo=FALSE, comment="", message=FALSE}
ALfitRushTDRnk<- lm(RushTd ~ Def.Rank.Yds, data = ALdf)
summary(ALfitRushTDRnk)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=17, data=ALdf)
RankLmPredictRt<- head(predict(ALfitRushTDRnk, CurrRank, interval="predict"),1)
RankLmPredictRt
```

Interceptions vs. Defensive Rank
```{r, echo=FALSE, comment="", message=FALSE}
ALfitIntRnk<- lm(Int ~ Def.Rank.Yds, data = ALdf)
summary(ALfitIntRnk)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE, comment="", message=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=17, data=ALdf)
RankLmPredictInt<- head(predict(ALfitIntRnk, CurrRank, interval="predict"),1)
RankLmPredictInt
```

## Machine Learning Alogorithm (Pass Yards)

### Data Splitting

In this data splitting action, I am splitting the data into 60% training set and 40% testing set.
```{r, echo=FALSE, comment="", message=FALSE}
library(caret)
library(lattice)

summary(ALdf)
inTrain <- createDataPartition(y=ALdf$PassYds,p=0.60, list=FALSE)
training <- ALdf[inTrain,]
testing <- ALdf[-inTrain,]
dim(training); dim(testing)
```

## K-Fold Cross Validation

We will then use the K-Fold process to cross-validate the data by splitting the training set in to many, smaller data sets.

Here, I am creating 10 folds and setting a random number seed of 32323 for the study. Each fold has approximately the same number of samples in it.
```{r, echo=FALSE, comment="", message=FALSE}
set.seed(32323)
Passfolds <- createFolds(y=ALdf$PassYds,k=10,list=TRUE,returnTrain=TRUE)
sapply(Passfolds,length)
Passfolds[[1]][1:10]
```

## Machine learning alogorithm decisioning

First I wanted to determine the optimal machine learning model to use.  The first test I used the Decision Tree approach.  I followed up by testing the Random Forest approach.

### Machine learning using Decision Trees

The first task was to determine model fit.
```{r, echo=FALSE, comment="", message=FALSE}
library(rpart)
modelFitPass <- rpart(PassYds ~ Def.Rank.Yds, data = ALdf, method = "anova")
```

Next, construct a Decision Tree graph
```{r, echo=FALSE, comment="", message=FALSE}
fancyRpartPlot(modelFitPass)
```

## Machine Learning Alogorithm (Rush Yards)

### Data Splitting

In this data splitting action, I am splitting the data into 60% training set and 40% testing set.
```{r, echo=FALSE, comment="", message=FALSE}
summary(ALdf)
inTrain <- createDataPartition(y=ALdf$RushYds,p=0.60, list=FALSE)
training <- ALdf[inTrain,]
testing <- ALdf[-inTrain,]
dim(training); dim(testing)
```

We will then use the K-Fold process to cross-validate the data by splitting the training set in to many, smaller data sets.

Here, I am creating 10 folds and setting a random number seed of 32323 for the study. Each fold has approximately the same number of samples in it.
```{r, echo=FALSE, comment="", message=FALSE}
set.seed(32323)
Passfolds <- createFolds(y=ALdf$RushYds,k=10,list=TRUE,returnTrain=TRUE)
sapply(Passfolds,length)
Passfolds[[1]][1:10]
```

Decision tree model fit Rush Yards Defense Rank.
```{r, echo=FALSE, comment="", message=FALSE}
modelFitRush <- rpart(RushYds ~ Def.Rank.Yds, data = ALdf, method = "anova")
```

Pass Yards decision tree graph
```{r, echo=FALSE, comment="", message=FALSE}
fancyRpartPlot(modelFitRush)
```


### Machine learning using Decision Trees

The first task was to determine model fit.
```{r, echo=FALSE, comment="", message=FALSE}
modelFitPass <- rpart(RushYds ~ Def.Rank.Yds, data = ALdf, method = "anova")
```

### Output from Decision Tree Model vs. Yards Passing

Current week (11) opponent Tennessee Titans.  The defense is currently ranked # 17 according to www.pro-football-reference.com.

According to the model, there is a 16% chance that Luck will pass for 313 yards.  This takes in to account defense rank ONLY.  There is an 24.0% chance Luck will rush for 17 yards.  Once again this takes in to account defense rank ONLY.

We will now use the LM model for prediction (Pass Yds)
```{r, echo=FALSE, comment="", message=FALSE}
lmModel<- lm(formula = PassYds ~ Opp+Def.Rank.Yds+Location+ConfGame, data = ALdf)
currdata = data.frame(Opp="TEN",Def.Rank.Yds=17,Location="Home",ConfGame="Conf",data=ALdf)
pass_predict_final<- head(predict(lmModel, currdata),1)
pass_predict_final
```

Predicted passing points
```{r, echo=FALSE, comment="", message=FALSE}
PassPts<-pass_predict_final*PassydsPts
PassPts
```

We will now use the LM model for prediction (Rush Yds)
```{r, echo=FALSE, comment="", message=FALSE}
lmModel<- lm(formula = RushYds ~ Opp+Def.Rank.Yds+Location+ConfGame, data = ALdf)
currdata = data.frame(Opp="TEN", Def.Rank.Yds=17, Location="Home", ConfGame="Conf",data=ALdf)
rush_predict_final<- head(predict(lmModel, currdata),1)
rush_predict_final
```

Predicted rushing points
```{r, echo=FALSE, comment="", message=FALSE}
RushPts<-rush_predict_final*RushydsPts
RushPts
```

We will now use the LM model for prediction (Pass TDs)
```{r, echo=FALSE, comment="", message=FALSE}
lmModel<- lm(formula = PassTD ~ Opp+Def.Rank.Yds+Location+ConfGame, data = ALdf)
currdata = data.frame(Opp="TEN", Def.Rank.Yds=17, Location="Home", ConfGame="Conf",data=ALdf)
passTd_predict_final<- head(predict(lmModel, currdata),1)
passTd_predict_final
```

Predicted rushing points
```{r, echo=FALSE, comment="", message=FALSE}
TdPassPts<-passTd_predict_final*PasstdPts
TdPassPts
```

We will now use the LM model for prediction (Rush TDs)
```{r, echo=FALSE, comment="", message=FALSE}
lmModel<- lm(formula = RushTd ~ Opp+Def.Rank.Yds+Location+ConfGame, data = ALdf)
currdata = data.frame(Opp="TEN", Def.Rank.Yds=17, Location="Home", ConfGame="Conf",data=ALdf)
rushTd_predict_final<- head(predict(lmModel, currdata),1)
rushTd_predict_final
```

Predicted rushing TD points
```{r, echo=FALSE, comment="", message=FALSE}
TdRushPts<-rushTd_predict_final*RushtdPts
TdRushPts
```

We will now use the LM model for prediction (Interceptions)
```{r, echo=FALSE, comment="", message=FALSE}
lmModel<- lm(formula = Int ~ Opp+Def.Rank.Yds+Location+ConfGame, data = ALdf)
currdata = data.frame(Opp="TEN", Def.Rank.Yds=17, Location="Home", ConfGame="Conf",data=ALdf)
Int_predict_final<- head(predict(lmModel, currdata),1)
Int_predict_final
```

Predicted rushing TD points
```{r, echo=FALSE, comment="", message=FALSE}
IntPts<-Int_predict_final*Int
IntPts
```

Total predicted points using linear regression models
```{r, echo=FALSE, comment="", message=FALSE}
CNTotalPer<- PassPts+RushPts+TdPassPts+TdRushPts+IntPts
CNTotalPer
```

Outcome:  Andrew Luck's predicted point total for Week 11 against the Tennessee Titans is 17.57 points.  NFL.com is predicting that Luck's point total will be 16.22 points

```{r, echo=FALSE, comment="", message=FALSE}
library(knitr)
knit("Luck_Quant Analysis_2016.Rmd")
```
