---
title: "Fantasy Football Team"
author: "Joshua Peterson"
date: "9/21/2016"
output:
  html_document: default
  word_document: default
---
Player analysis and selection for the week of 09.19.2016

```{r Points, echo=FALSE}
PassydsPts<- 1/25
PasstdPts<- 4
Int<- -2
RushydsPts<- 1/10
RushtdPts<- 6
```

QB Analysis - Pull Player Data
```{r QB, echo=FALSE}
CN<- read.csv("Cam Newton.csv")
CNdf<- as.data.frame(CN)
```

# QB Analysis

## Cam Newton - Summary Passing Data

Newton Yards Summary
```{r Newton Passing, echo=FALSE}
summary(CNdf)

```

## Exploratory data analysis

### Location analysis

```{r}
par(mfrow = c(5,2), mar = c(4,4,1,1))
plot(CNdf$Location, CNdf$PassYds, ylab = "Passing Yards", col = "red")
plot(CNdf$Location, CNdf$RushYds, ylab = "Rushing Yards", col = "blue")
plot(CNdf$Location, CNdf$PassTD, ylab = "Passing TDs", col = "green")
plot(CNdf$Location, CNdf$RushTD, ylab = "Rushing TDs", col = "purple")
plot(CNdf$Location, CNdf$Int, ylab = "Interceptions", col = "grey")

```

### Opponent Analysis

Opponent vs. Pass Yards
```{r}
par(mfrow = c(5,1), mar = c(4,4,1,1))
plot(CNdf$Opp, CNdf$PassYds, ylab = "Yards Passing", xlab = "Opponent", col = "red")
plot(CNdf$Opp, CNdf$RushYds, ylab = "Yards Rushing", xlab = "Opponent", col = "blue")
plot(CNdf$Opp, CNdf$PassTD, ylab = "Passing TDs", xlab = "Opponent", col = "green")
plot(CNdf$Opp, CNdf$RushTD, ylab = "Rushing TDs", xlab = "Opponent", col = "purple")
plot(CNdf$Opp, CNdf$Int, ylab = "Interceptions", xlab = "Opponent", col = "grey")
```

### Defensive Ranking Analysis

Defense rank vs. Pass Yards
```{r}
library(ggplot2)
par(mfrow = c(5,2), mar = c(4,4,1,1))
qplot(Def.Rank.Yds,PassYds, data = CNdf) + geom_smooth(method = "lm")
qplot(Def.Rank.Yds, RushYds, data = CNdf) + geom_smooth(method = "lm")
qplot(Def.Rank.Yds, PassTD, data = CNdf) + geom_smooth(method = "lm")
qplot(Def.Rank.Yds, RushTD, data = CNdf) + geom_smooth(method = "lm")
qplot(Def.Rank.Yds, Int, data = CNdf) + geom_smooth(method = "lm")
```






Newton Yards LSE
```{r Newton LSE, echo=FALSE}
par(mfrow = c(3,2), mar = c(4,4,2,1))
hist(CNdf$PassYds,col="blue",breaks=100, main = "Histogram of Newton Pass Yds/Game",xlab = "Yards/Game")
hist(CNdf$RushYds,col="red",breaks=100, main = "Histogram of Newton Rush Yds/Game",xlab = "Yards/Game")  
hist(CNdf$PassTD,col="purple",breaks=100, main = "Histogram of Newton Pass TDs/Game",xlab = "TDs/Game")
hist(CNdf$RushTD,col="grey",breaks=100, main = "Histogram of Newton Rush TDs/Game",xlab = "TDs/Game")
hist(CNdf$Int,col="grey",breaks=100, main = "Histogram of Newton Interceptions/Game",xlab = "Interceptions/Game")
```


## Linear model fitting

### Model fitting vs. Location

Pass Yds vs. Location
```{r, echo=FALSE}
CNfitPassYdsLoc<- lm(PassYds ~ Location, data = CNdf)
summary(CNfitPassYdsLoc)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrLoc<- data.frame(Location="Away", data=CNdf)
LocLmPredictPy<- head(predict(CNfitPassYdsLoc, CurrLoc, interval="predict"))
LocLmPredictPy
```



Rush Yds. vs. Location
```{r}
CNfitRushYdsLoc<- lm(RushYds ~ Location, data = CNdf)
summary(CNfitRushYdsLoc)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrLoc<- data.frame(Location="Away", data=CNdf)
LocLmPredictRy<- head(predict(CNfitRushYdsLoc, CurrLoc, interval="predict"))
LocLmPredictRy
```

Pass TDs. vs. Location
```{r, echo=FALSE}
CNfitPassTDLoc<- lm(PassTD ~ Location, data = CNdf)
summary(CNfitPassTDLoc)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrLoc<- data.frame(Location="Away", data=CNdf)
LocLmPredictPt<- head(predict(CNfitPassTDLoc, CurrLoc, interval="predict"))
LocLmPredictPt
```

Rush TDs vs. Location
```{r, echo=FALSE}
CNfitRushTDLoc<- lm(RushTD ~ Location, data = CNdf)
summary(CNfitRushTDLoc)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrLoc<- data.frame(Location="Away", data=CNdf)
LocLmPredictRt<- head(predict(CNfitRushTDLoc, CurrLoc, interval="predict"))
LocLmPredictRt
```


#### Model fitting vs. opponent

Pass Yards vs. opponent data
```{r}
CNfitPassYds<- lm(PassYds ~ Opp, data = CNdf)
summary(CNfitPassYds)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrOpp<- data.frame(Opp="STL", data=CNdf)
OppLmPredictPy<- head(predict(CNfitPassYds, CurrOpp, interval="predict"))
OppLmPredictPy
```

Rush Yards vs. opponent data

```{r}
CNfitRushYds<- lm(RushYds ~ Opp, data = CNdf)
summary(CNfitRushYds)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrOpp<- data.frame(Opp="STL", data=CNdf)
OppLmPredictRy<- head(predict(CNfitRushYds, CurrOpp, interval="predict"))
OppLmPredictRy
```

Pass TDs vs. opponent data
```{r}
CNfitPassTD<- lm(PassTD ~ Opp, data = CNdf)
summary(CNfitPassTD)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrOpp<- data.frame(Opp="STL", data=CNdf)
OppLmPredictPt<- head(predict(CNfitPassTD, CurrOpp, interval="predict"))
OppLmPredictPt
```

Rush TDs vs. opponent data
```{r}
CNfitRushTD<- lm(RushTD ~ Opp, data = CNdf)
summary(CNfitRushTD)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrOpp<- data.frame(Opp="STL", data=CNdf)
OppLmPredictRt<- head(predict(CNfitRushTD, CurrOpp, interval="predict"))
OppLmPredictRt
```

Interceptions vs. opponent data
```{r}
CNfitInt<- lm(Int ~ Opp, data = CNdf)
summary(CNfitInt)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrOpp<- data.frame(Opp="STL", data=CNdf)
OppLmPredictInt<- head(predict(CNfitInt, CurrOpp, interval="predict"))
OppLmPredictInt
```

### Model fitting vs. defensive rank

Pass Yards vs. Defensive Rank
```{r, echo=FALSE}
CNfitPassYdsRnk<- lm(PassYds ~ Def.Rank.Yds, data = CNdf)
summary(CNfitPassYdsRnk)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=10, data=CNdf)
RankLmPredictPy<- head(predict(CNfitPassYdsRnk, CurrRank, interval="predict"))
RankLmPredictPy
```

Rush Yards vs. Defensive Rank
```{r, echo=FALSE}
CNfitRushYdsRnk<- lm(RushYds ~ Def.Rank.Yds, data = CNdf)
summary(CNfitRushYdsRnk)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=10, data=CNdf)
RankLmPredictRy<- head(predict(CNfitRushYdsRnk, CurrRank, interval="predict"))
RankLmPredictRy
```

Pass TDs vs. Defensive Rank
```{r, echo=FALSE}
CNfitPassTDRnk<- lm(PassTD ~ Def.Rank.Yds, data = CNdf)
summary(CNfitPassTDRnk)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=10, data=CNdf)
RankLmPredictPt<- head(predict(CNfitPassTDRnk, CurrRank, interval="predict"))
RankLmPredictPt
```

Rush TDs vs. Defensive Rank
```{r, echo=FALSE}
CNfitRushTDRnk<- lm(RushTD ~ Def.Rank.Yds, data = CNdf)
summary(CNfitRushTDRnk)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=10, data=CNdf)
RankLmPredictRt<- head(predict(CNfitRushTDRnk, CurrRank, interval="predict"))
RankLmPredictRt
```

Interceptions vs. Defensive Rank
```{r, echo=FALSE}
CNfitIntRnk<- lm(Int ~ Def.Rank.Yds, data = CNdf)
summary(CNfitIntRnk)$coefficients
```

Prediction interval using a linear model
```{r, echo=FALSE}
CurrRank<- data.frame(Def.Rank.Yds=10, data=CNdf)
RankLmPredictInt<- head(predict(CNfitIntRnk, CurrRank, interval="predict"))
RankLmPredictInt
```




###Newton Pass Yards Plot of Data Yards against opponents
```{r, echo=FALSE}
PYplotOpp<- ggplot(CNdf, aes(x=PassYds, y=Opp))
PYplotOpp=PYplotOpp + geom_point(size = 7, colour = "black", alpha = 0.2)
PYplotOpp=PYplotOpp + geom_smooth(method = "lm", colour = "black")
PYplotOpp
```

Newton Rush Yards Plot of Data Yards against opponents
```{r, echo=FALSE}
RYplotOpp<- ggplot(CNdf, aes(x=RushYds, y=Opp))
RYplotOpp=RYplotOpp + geom_point(size = 7, colour = "black", alpha = 0.2)
RYplotOpp=RYplotOpp + geom_smooth(method = "lm", colour = "black")
RYplotOpp
```

Newton TDs Plot of Data Yards against opponents
```{r, echo=FALSE}
TDplotOpp<- ggplot(CNdf, aes(x=PassTD, y=Opp))
TDplotOpp=TDplotOpp + geom_point(size = 7, colour = "black", alpha = 0.2)
TDplotOpp=TDplotOpp + geom_smooth(method = "lm", colour = "black")
TDplotOpp
```


## Machine Learning Alogorithm (Pass Yards)

### Data Splitting

In this data splitting action, I am splitting the data into 60% training set and 40% testing set.
```{r, echo=FALSE}
summary(CNdf)
inTrain <- createDataPartition(y=CNdf$PassYds,p=0.60, list=FALSE)
training <- CNdf[inTrain,]
testing <- CNdf[-inTrain,]
dim(training); dim(testing)
```

## K-Fold Cross Validation

We will then use the K-Fold process to cross-validate the data by splitting the training set in to many, smaller data sets.

Here, I am creating 10 folds and setting a random number seed of 32323 for the study. Each fold has approximately the same number of samples in it.
```{r}
set.seed(32323)
Passfolds <- createFolds(y=CNdf$PassYds,k=10,list=TRUE,returnTrain=TRUE)
sapply(Passfolds,length)
Passfolds[[1]][1:10]
```

## Machine learning alogorithm decisioning

First I wanted to determine the optimal machine learning model to use.  The first test I used the Decision Tree approach.  I followed up by testing the Random Forest approach.

### Machine learning using Decision Trees

The first task was to determine model fit.
```{r, echo=FALSE}
library(rpart)
modelFitPass <- rpart(PassYds ~ Def.Rank.Yds, data = CNdf, method = "anova")
```

Next, construct a Decision Tree graph
```{r}
fancyRpartPlot(modelFitPass)
```

## Machine Learning Alogorithm (Rush Yards)

### Data Splitting

In this data splitting action, I am splitting the data into 60% training set and 40% testing set.
```{r, echo=FALSE}
summary(CNdf)
inTrain <- createDataPartition(y=CNdf$RushYds,p=0.60, list=FALSE)
training <- CNdf[inTrain,]
testing <- CNdf[-inTrain,]
dim(training); dim(testing)
```

We will then use the K-Fold process to cross-validate the data by splitting the training set in to many, smaller data sets.

Here, I am creating 10 folds and setting a random number seed of 32323 for the study. Each fold has approximately the same number of samples in it.
```{r}
set.seed(32323)
Passfolds <- createFolds(y=CNdf$RushYds,k=10,list=TRUE,returnTrain=TRUE)
sapply(Passfolds,length)
Passfolds[[1]][1:10]
```

Decision tree model fit Rush Yards Defense Rank.
```{r, echo=FALSE}
modelFitRush <- rpart(RushYds ~ Def.Rank.Yds, data = CNdf, method = "anova")
```

Pass Yards decision tree graph
```{r}
fancyRpartPlot(modelFitRush)
```


### Machine learning using Decision Trees

The first task was to determine model fit.
```{r, echo=FALSE}
modelFitPass <- rpart(RushYds ~ Def.Rank.Yds, data = CNdf, method = "anova")
```

### Output from Decision Tree Model vs. Yards Passing

Current week (9) opponent L.A. Rams (formerly St. Louis Rams).  The defense is currently ranked # 10 according to www.pro-football-reference.com.

According to the model, there is a 60% chance that Cam Newton will pass for 240 yards.  This takes in to account defense rank ONLY.  There is an 18.0% chance Cam will rush for 25 yards.  Once again this takes in to account defense rank ONLY.

We will now use the LM model for prediction (Pass Yds)
```{r, echo=FALSE}
lmModel<- lm(formula = PassYds ~ Opp+Def.Rank.Yds+Location, data = CNdf)
currdata = data.frame(Opp="STL", Def.Rank.Yds=10, Location="Home",data=CNdf)
pass_predict_final<- predict(lmModel, currdata)
pass_predict_final
```

Predicted passing points
```{r, echo=FALSE}
PassPts<-pass_predict_final*PassydsPts
PassPts
```

We will now use the LM model for prediction (Rush Yds)
```{r, echo=FALSE}
lmModel<- lm(formula = RushYds ~ Opp+Def.Rank.Yds+Location, data = CNdf)
currdata = data.frame(Opp="STL", Def.Rank.Yds=10, Location="Home",data=CNdf)
rush_predict_final<- predict(lmModel, currdata)
rush_predict_final
```

Predicted rushing points
```{r, echo=FALSE}
RushPts<-rush_predict_final*RushydsPts
RushPts
```

We will now use the LM model for prediction (Pass TDs)
```{r, echo=FALSE}
lmModel<- lm(formula = PassTD ~ Opp+Def.Rank.Yds+Location, data = CNdf)
currdata = data.frame(Opp="STL", Def.Rank.Yds=10, Location="Home",data=CNdf)
passTd_predict_final<- predict(lmModel, currdata)
passTd_predict_final
```

Predicted rushing points
```{r, echo=FALSE}
TdPassPts<-passTd_predict_final*PasstdPts
TdPassPts
```

We will now use the LM model for prediction (Rush TDs)
```{r, echo=FALSE}
lmModel<- lm(formula = RushTD ~ Opp+Def.Rank.Yds+Location, data = CNdf)
currdata = data.frame(Opp="STL", Def.Rank.Yds=10, Location="Home",data=CNdf)
rushTd_predict_final<- predict(lmModel, currdata)
rushTd_predict_final
```

Predicted rushing TD points
```{r, echo=FALSE}
TdRushPts<-rushTd_predict_final*RushtdPts
TdRushPts
```

Total predicted points using linear regression models
```{r, echo=FALSE}
CNTotalPer<- PassPts+RushPts+TdPassPts+TdRushPts
CNTotalPer
```

Outcome:  Cam Newton's predicted point total for Week 9 against the LA Rams is 13.21 points.  NFL.com is predicting that Cam's point total will be 15.44 points

```{r, echo=FALSE}
library(knitr)
knit("QB_ML_Experiment_2016.Rmd")
```